%-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-%
% CS 196 Copyrights and Patents Survey
% 
% Typeset with the `acmlarge` template by Donald Knuth & Leslie Lamport
% 
% Copyright 2016 Fiestada, Lobaton, Dacuba, Cañedo, Latoga
% For more information about this survey, go to https://cs196copyrights.github.io/survey
% or email the Git repo maintainer at vffiestada@up.edu.ph
%
%-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-/`-%
\documentclass[prodmode,cs196]{acmlarge}

% Metadata Information
\acmVolume{1}
\acmNumber{1}
\acmArticle{2}
\articleSeq{1}
\acmYear{2016}
\acmMonth{09}

% Page heads
\markboth{Canedo, Dacuba, Fiestada, Latoga, and Lobaton}{Opinions of UP Diliman Students on Technology Copyrights and Patents}

% Title portion
\title{Opinions of UP Diliman Students on Technology Copyrights and Patents}
\author{ABBY CANEDO, CARISSE DACUBA, VINCENT FIESTADA, AREL LATOGA, and TROI LOBATON \affil{University of the Philippines Diliman}}

\begin{abstract}
In this paper, the authors take a look at the popular opinion of University of the
Philippines Diliman Students, particularly those pursuing Engineering and
Science degrees, regarding technological copyrights and patents. In particular, this paper
examines their opinions on the extent of influence that a particular piece of design
or feature has on a whole product. This is done in the context of the Samsung
vs. Apple and Oracle vs. Google trials about their similar products.
\end{abstract}

\category{Ethical and Professional Issues}{Technology and Computing}{Popular views and opinions}[Surveys and Analysis]

\terms{Patents \and Copyrights}
\keywords{Ethics, patents, copyrights, technology, computing}

\acmformat{Canedo, Dacuba, Fiestada, Latoga, and Lobaton. 2016. Opinions of UP Diliman students on technology copyrights and patents.}

\begin{document}

\begin{bottomstuff}
\copyright Copyright 2016 Canedo, Dacuba, Fiestada, Latoga, and Lobaton.
\end{bottomstuff}


\maketitle

% Head 1
\section{Introduction}

Technological patents and copyrights have posed 

\section{Methodology}

\end{document}